Biden Projected to Win in the 2024 US Presidential Election

### 2024-03-15 paper/paper.qmd
made changes to the introduction section

---
title: "Biden Projected to Win in the 2024 US Presidential Election"
author:
  - Monica Sainani
  - Kaavya Kalani
thanks: "Code and data supporting this analysis is available at: https://github.com/sainanim/Predictions-for-the-US-2024-Elections"
date: today
date-format: long
abstract: "This study investigates the dynamics of voting behaviour of americans leveraging demographic, socioeconomic, and geographic factors, such as age, family income, education, state of residency, and sex. We use a Bayesian Logistic Regression model with Post-Stratification to predict the outcome between Biden and Trump with the mentioned factors as predictors. Our study indictates that Biden is likely to be re-elected as the president with a 10% lead. This research contributes to a better understanding of the factors influencing political engagement in American democracy by offering insightful information that might guide future electoral strategies and policy discussion."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

>>>>

---
title: "Biden Projected to Win in the 2024 US Presidential Election"
author:
  - Monica Sainani
  - Kaavya Kalani
thanks: "Code and data supporting this analysis is available at: https://github.com/sainanim/Predictions-for-the-US-2024-Elections"
date: today
date-format: long
abstract: "This study investigates the dynamics of voting behaviour of Americans leveraging demographic, socioeconomic,
and geographic factors, such as age, family income, education, state of residency, and sex. We use a Bayesian Logistic
Regression model with Post-Stratification to predict the outcome between Biden and Trump with the mentioned factors as
predictors. Our study indicates that Biden is likely to be re-elected as the president with a 10% lead. This research
contributes to a better understanding of the factors influencing political engagement in American democracy by offering
insightful information that might guide future electoral strategies and policy discussion."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---
